Adopting agile in the large: motivations, success factors and challenges

### 2014-05-17 journal/article.tex
Editing: Large-scale hyphen

agile \sep transformation \sep large scale \sep adopting agile

@@

--> Why is large scale software development different from smaller scale?

@@

\item
RQ1: Why do large organizations initiate an agile transformation?

\item
RQ2: How do large scale agile transformations usually proceed?

\item
RQ3: What are typical successes and challenges in a large scale agile
     transformation process?

@@

The facet of \emph{organizational transformation} was interpreted so that the
primary study must present insights on the process of transformation. This
was the most important facet, as the pivot of this research is to examine
how the transformations happen. Examples on excluded topics are comparing the
original and agile development methods \cite{Petersen2010}, discussing use of
agile in a large organization but not describing how the new methods were
introduced \cite{Mishra2011}, and merely presenting agile tools in large scale
use \cite{Kim2012}. These sources were excluded as they did not privide insights
on organizational transformation.
% Also [Fitzgerald 2005] on just presenting use of agile methods, no introducing

@@

The facet of \emph{large scale} was interpreted as presented in section
\ref{sec:largescale}, having 50 development personel or 6 teams as as the limit
for large scale. In some cases the source presented very vague indicators on
size. For instance, we deemed the case presented by Cloke \cite{Cloke2007} to be
included as there was indications of large scale considerations, although the
size remained unclear. The case presented by Miller and Haddad \cite{Miller2012}
was deemed to be excluded as there was no indications whatsoever on size. A
borderline exclude was the case presented by Tudor \cite{Tudor2006} as there was
no indication of issues indicating large size, althoug there were several
development teams.
To complicate matters, some papers talked about ``the team'' in singular when
referring to the organization \cite{Hodgkins2007}, making it clearly nontrivial
to judge whether an organization was large based on the choice of words of the
author.

@@

Large scale definition & A definition of "large scale" software development. \\

@@

* Transformation and scaling up are connected concepts. Although this research
  focuses on transformation process only, it can not be completely separated
  from discussion on scaling up, or on large scale agile implementation in
  general.

* Transformation of an organization to use agile can be seen as transforming
  also the agile method to suit the organization.
  --> A large scale agile model may require tailoring and trial over time

@@

* Compare how recommendations in large scale application models of agile relate
  to the challenges and success factors reported in the transformaiton proecss.

>>>>

agile \sep transformation \sep large-scale \sep adopting agile

@@

--> Why is large-scale software development different from smaller scale?

@@

\item
RQ1: Why do large software development organizations initiate an agile
transformation?

\item
RQ2: How do large-scale agile transformations usually proceed?

\item
RQ3: What are typical successes and challenges in a large-scale agile
     transformation process?

@@

The facet of \emph{organizational transformation} was interpreted so that the
primary study must present insights on the process of transformation. This
was the most important facet, as the pivot of this research is to examine
how the transformations happen. Examples on excluded topics are comparing the
original and agile development methods \cite{Petersen2010}, discussing use of
agile in a large organization but not describing how the new methods were
introduced \cite{Mishra2011}, and merely presenting agile tools in large-scale
use \cite{Kim2012}. These sources were excluded as they did not privide insights
on organizational transformation.
% Also [Fitzgerald 2005] on just presenting use of agile methods, no introducing

@@

The facet of \emph{large scale} was interpreted as presented in section
\ref{sec:largescale}, having 50 development personel or 6 teams as as the limit
for large scale. In some cases the source presented very vague indicators on
size. For instance, we deemed the case presented by Cloke \cite{Cloke2007} to be
included as there was indications of large-scale considerations, although the
size remained unclear. The case presented by Miller and Haddad \cite{Miller2012}
was deemed to be excluded as there was no indications whatsoever on size. A
borderline exclude was the case presented by Tudor \cite{Tudor2006} as there was
no indication of issues indicating large size, althoug there were several
development teams.
To complicate matters, some papers talked about ``the team'' in singular when
referring to the organization \cite{Hodgkins2007}, making it clearly nontrivial
to judge whether an organization was large based on the choice of words of the
author.

@@

Large scale definition & A definition of large-scale software development. \\

@@

* Transformation and scaling up are connected concepts. Although this research
  focuses on transformation process only, it can not be completely separated
  from discussion on scaling up, or on large-scale agile implementation in
  general.

* Transformation of an organization to use agile can be seen as transforming
  also the agile method to suit the organization.
  --> A large-scale agile model may require tailoring and trial over time

@@

* Compare how recommendations in large-scale application models of agile relate
  to the challenges and success factors reported in the transformaiton proecss.
